---
title: "Getting started with CatchAll"
author: Amy Willis
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`CatchAll` is a package for species richness estimation and modelling. It is based off the original CatchAll software program by Bunge et. al, but now coded into R and updated to reflect new use cases.

At this point, only the Poisson model is available to use. Here is an example of its use

```{r}
### Run the first two lines at home! ####
# install.packages("devtools")
# devtools::install_github("adw96/CatchAll")
library(devtools)
library(CatchAll)
library(magrittr)
devtools::install_github("adw96/breakaway")
library(breakaway)
set.seed(1)
counts <- rpois(5000, 2)
PoissonModel(counts, cutoff = 10)
```
Not too bad, given that the true richness is 5000!

Let's try another cutoff:
```{r}
PoissonModel(counts)
```

Now run all models!
```{r}
# suppressMessages({y <- CatchAll(counts)})
# head(y)
```
